The Decline in U.S Birthrates in Recent Years is Indicative of Cultural and Economic Changes

### 2022-02-28 Output/paper 2.Rmd
Final changes.

We created a variable for the total number of births by adding up all the births by state and then grouping them by year. We also created a variable that stated the total population of each race-age combination by similar methods. We obtained a variable that got the percentage of population of a demographic by dividing the sum of that demographic by the total population and multiplying by 100. We produced a variable of contribution to total birth rate decline by subtracting 2019 birth rates of the age group from the 2000 birth rates of the same age group and dividing that by the total birthrate value for 2000, then multiplying by 200. We got the variables for all our explanatory factors by grouping them by year and getting the mean values from all the states. For the average debt, we multiplied by 10,000 as that is how it was shown in the original source. We got the variable on the importance of religion by dividing the number of people who felt religion was important over the total number surveys. Note that for these variables we needed to use 2004 data as 2000 data was not available.

>>>>

We created a variable for the total number of births by adding up all the births by state and then grouping them by year. We also created a variable that stated the total population of each race-age combination by similar methods. We obtained a variable that got the percentage of population of a demographic by dividing the sum of that demographic by the total population and multiplying by 100. We produced a variable of contribution to total birth rate decline by subtracting 2019 birth rates of the age group from the 2000 birth rates of the same age group and dividing that by the total birthrate value for 2000, then multiplying by 200. We got the variables for all our explanatory factors by grouping them by year and getting the mean values from all the states. For the average debt, we multiplied by 10,000 as that is how it was shown in the original source. We got the variable on the importance of religion by dividing the percentage of people who felt religion was important over the total percentage of people surveyed. Note that for these variables we needed to use 2004 data as 2000 data was not available.
